evaluating_enet_penalization_parameters

### 2019-05-22 Scripts/comparing_distance_profiles_using_density_plots.Rmd
results scripts

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(coin)
```

@@

ggplot(all_dist_gm12878, aes(x = Resolution, y = value, fill = y)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(#fill = fill, 
               #colour = line,
               outlier.shape = NA) +
  facet_grid(~ variable) +
  xlab("Resolution") +
  ylab("Log2 Distances") +
  ylim(5,25) +
  scale_fill_discrete(name="Class of Genomic Bin",
                      labels=c("Did not overlap\nw/ flanked TAD boundary",
                               "Overlapped\nw/ flanked TAD boundary")) +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))
```

@@

ggplot(all_dist_K562, aes(x = Resolution, y = value, fill = y)) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot(#fill = fill, 
               #colour = line,
               outlier.shape = NA) +
  facet_grid(~ variable) +
  xlab("Resolution") +
  ylab("Log2 Distances") +
  ylim(5,25) +
  scale_fill_discrete(name="Class of Genomic Bin",
                      labels=c("Did not overlap\nw/ flanked TAD boundary",
                               "Overlapped\nw/ flanked TAD boundary")) +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))
```

>>>>

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(coin)
library(ggsignif)
```

@@

# 10 kb
all_dist_gm12878_10kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("Transcription Factor\nBinding Site") +
  ylab("Log2 Distance") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 25 kb
all_dist_gm12878_25kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 50 kb
all_dist_gm12878_50kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 100 kb
all_dist_gm12878_100kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

figure <- ggarrange(all_dist_gm12878_25kb,
                    all_dist_gm12878_50kb,
                    all_dist_gm12878_100kb,
                    ncol = 1,
                    nrow = 3,
                    common.legend = TRUE,
                    legend = "top",
                    labels = "AUTO",
                    font.label = list(size=20))
figure 
annotate_figure(figure, 
                bottom = text_grob("Transcription Factor\nBinding Site", color = "black", size = 20),
                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
```

@@

# 10 kb
all_dist_K562_10kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 25 kb
all_dist_K562_25kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 50 kb
all_dist_K562_50kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 100 kb
all_dist_K562_100kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

figure <- ggarrange(all_dist_K562_10kb,
                    all_dist_K562_25kb,
                    all_dist_K562_50kb,
                    all_dist_K562_100kb,
                    ncol = 2,
                    nrow = 2,
                    common.legend = TRUE,
                    legend = "top",
                    labels = "AUTO",
                    font.label = list(size=20))
figure 
annotate_figure(figure, 
                bottom = text_grob("Transcription Factor\nBinding Site", color = "black", size = 20),
                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
```

### 2019-05-22 Scripts/comparing_enet_and random_forest.Rmd
results scripts

ggplot(all_enetperfs_mcc, aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

ggplot(all_enetperfs_f1, aes(x=Resolution, y=F1, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

ggplot(all_enetperfs_auprc, aes(x=Resolution, y=AUPRC, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
```

>>>>

mccplot <- ggplot(all_enetperfs_mcc, aes(x=Resolution, y=MCC, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=MCC-MCCSD, ymax=MCC+MCCSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

f1plot <- ggplot(all_enetperfs_f1, aes(x=Resolution, y=F1, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=F1-F1SD, ymax=F1+F1SD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

@@

auprcplot <- ggplot(all_enetperfs_auprc, aes(x=Resolution, y=AUPRC, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

figure <- ggarrange(mccplot,
                    f1plot,
                    auprcplot,
                    ncol=1,
                    nrow=3,
                    common.legend = TRUE,
                    legend = "top")
figure
```

### 2019-05-22 Scripts/evaluating_enet_penalization_parameters.Rmd
results scripts

#alpha
ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=alpha, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=alpha-alphaSD, ymax=alpha+alphaSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#lambda
ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=lambda, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=lambda-lambdaSD, ymax=lambda+lambdaSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
```

>>>>

#alpha
alphaplot <- ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=alpha, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=alpha-alphaSD, ymax=alpha+alphaSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#lambda
lambdaplot <- ggplot(penal_params_gm12878_summ, aes(x=Resolution, y=lambda, color=Resampling, group=Resampling)) +
     geom_line(size=2, position=position_dodge(0.5))+
     geom_point(size=5, position=position_dodge(0.5))+
     geom_errorbar(aes(ymin=lambda-lambdaSD, ymax=lambda+lambdaSD), width=1,
                 position=position_dodge(0.5)) +
     facet_grid(~ Predictor)+
     theme_minimal() +
     theme_bw()+
     #xlab("") + ylab("") + #ylim(-.05,.5) +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

figure <- ggarrange(alphaplot,
                    lambdaplot,
                    ncol = 1,
                    nrow = 2,
                    common.legend = TRUE,
                    legend = "top")
figure
```
